Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-08-04 writing/DraftExposurePaper/DraftExposurePaper.Rmd
rearrange code sections for wind plots
add plot for baltimore county comparison

>>>>

Compare data from `countyweather` and NLDAS-2 data for Baltimore county by storm:

```{r}
check_dates <- dplyr::select(closest_dist, -storm_dist) %>%
        dplyr::mutate(closest_date = ymd(closest_date)) %>%
        dplyr::rename(day_0 = closest_date) %>%
        dplyr::mutate(fips = as.integer(fips),
                      day_0 = day_0 + days(0),
                      day_b1 = day_0 - days(1),
                      day_b2 = day_0 - days(2),
                      day_a1 = day_0 + days(1),
                      day_a2 = day_0 + days(2),
                      day_a3 = day_0 + days(3)) %>%
        dplyr::select(storm_id, fips, day_b2, day_b1,
                      day_0, day_a1, day_a2, day_a3) %>%
        tidyr::gather(key = lag, value = day, -storm_id, -fips) %>%
        dplyr::rename(date = day) %>%
        dplyr::filter(fips == "24005") %>%
        dplyr::mutate(fips = as.character(fips))
        #dplyr::mutate(day = as.numeric(format(day, "%Y%m%d")))

fips <- "24005"
# I've commented this out because we're saving the data, so we only need
# to run it once.
# county_timeseries(fips, percent_coverage = 0,
#                   date_min = "1988-01-01", date_max = "2011-12-31",
#                   var = "PRCP",
#                   out_directory = "baltimore_data/")

baltimore_dir <- "baltimore_data/"
baltimore_weather <- readRDS(paste0(baltimore_dir, fips, ".rds"))

baltimore_weather <- baltimore_weather %>%
        filter(date %in% seq(from = as.Date("1988-01-01"), to = as.Date("2011-12-31"), by = 1))

baltimore_weather$fips <- fips
baltimore_weather <- as.data.frame(baltimore_weather)

baltimore_weather <- baltimore_weather %>%
        dplyr::filter(date %in% all_dates) %>%
        dplyr::right_join(data.table(check_dates),
                          by = c("fips" = "fips", "date" = "date")) %>%
        dplyr::filter(!is.na(prcp)) %>%
        dplyr::arrange(storm_id, fips) %>%
        dplyr::mutate(fips = as.integer(fips)) %>%
        dplyr::mutate(fips = sprintf("%05d", fips),
                      lag = gsub("day_", "", lag),
                      lag = gsub("b", "-", lag),
                      lag = gsub("a", "", lag),
                      lag = as.numeric(lag))

baltimore_rain <- countyweather_rain(counties = fips, county_weather = baltimore_weather,
                                 start_year = 1988, end_year = 2011,
                                 rain_limit = 0, dist_limit = 2000)
baltimore_plot <- ggplot(baltimore_rain, aes(x = cw_precip, y = tot_precip)) +
        geom_hline(aes(yintercept = 75), color = "lightgray") +
        geom_vline(aes(xintercept = 75), color = "lightgray") +
        geom_abline(aes(intercept = 0, slope = 1), color = "gray", alpha = 0.5) +
        # geom_point(aes(size = prcp_reporting), alpha = 0.2) +
        geom_point(alpha = 0.5) +
        # geom_text(aes(x = monitor_rain + 100, label = storm_id)) +
        xlim(c(0, 275)) + ylim(c(0, 275)) +
        theme_few() +
        scale_size_continuous(guide = "none") +
        xlab("Rainfall (mm) based on \naveraged county monitors") +
        ylab("Rainfall (mm) based on \nNLDAS-2 county data") +
        ggtitle("Monitor versus NLDAS rainfall estimates \nfor Baltimore county, MD, by storm")

baltimore_plot
```
